artData

### 2018-02-08 docs/articles/dataMaid_artData.Rmd
CSP 2018 website

---
dataMaid: yes
title: artData
subtitle: "Autogenerated data summary from dataMaid"
date: 2018-02-08 11:55:28
output: html_document
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
```{r visualFunctions, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report overview
The dataset examined has the following dimensions:

@@

 *  Report creation time: Thu Feb 08 2018 11:55:29

>>>>

---
dataMaid: yes
title: artData
subtitle: "Autogenerated data summary from dataMaid"
date: 2018-02-08 12:00:56
output: html_document
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
```{r visualFunctions, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report overview
The dataset examined has the following dimensions:

@@

 *  Report creation time: Thu Feb 08 2018 12:00:56
